Update of the ozone dry deposition in the OsloCTM3 v1.0

### 2018-11-06 DryDep.tex
Started to include the actual resuls into the documents and updated some plots.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%      
\section{Evaluation}
\label{sec:eval}
For meteorological input, we use \href{https://www.ecmwf.int/en/forecasts/documentation-and-support/evolution-ifs/cycle-38r1-summary-changes}{ECMWF - OpenIFS version cy38r1nc4}. CEDS historical emission inventory is used for emissions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sensitivity tests}
\label{subsec:sens}
Include table of all sensitivity runs.
\citep[e.g., $v^\chem{O_3}_{ice/snow} = 1/10000\,\unit{cm\,s^{-1}}$,][]{ACP:Helmig2007}
dry dep velocity over water \citep{JGR:Helmig2012} Impact of ocean? Although it is a low number there is 2\/3 ocean on earth... (Think, I read this in Hardacre paper... -> Luhar)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with recent multi-model comparison}
\label{subsec:model}
Compare to \citet{ACP:Hardacre2015} as well as \citet{ACP:Luhar2017}. \citep{AE:Derwent2018} Uncertainties in surface ozone sources and sinks larger than in formulations? -> Need to read this one...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with observations}
\label{subsec:obs}
The sites used in \citet{ACP:Hardacre2015} and additional ozone zonal data from satellites and sondes (\url{http://bodekerscientific.com/}). \citep{AE:Hu2017} -> need to look into this one...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
\label{sec:disc}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%      
\section{Evaluation}
\label{sec:eval}
For meteorological input, we use \href{https://www.ecmwf.int/en/forecasts/documentation-and-support/evolution-ifs/cycle-38r1-summary-changes}{ECMWF - OpenIFS version cy38r1nc4}. CEDS historical emission inventory is used for emissions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sensitivity tests}
\label{subsec:sens}
Include table of all sensitivity runs.
\citep[e.g., $v^\chem{O_3}_\text{ice/snow} = 1/10000\,\unit{cm\,s^{-1}}$,][]{ACP:Helmig2007}
dry dep velocity over water \citep{JGR:Helmig2012} Impact of ocean? Although it is a low number there is 2\/3 ocean on earth... (Think, I read this in Hardacre paper... -> Luhar)

\begin{figure}[t]
  \includegraphics[width=8.3cm]{pictures/final-ozone_diff_maps}
  \caption{Relative difference between the sensitivity simulation emep\_psgsssh and the Wesely scheme in (a) surface ozone concentration; (b) ozone dry deposition velosity; (c) amount of ozone removed from the atmosphere by dry deposition.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with recent multi-model comparison}
\label{subsec:model}
Compare to \citet{ACP:Hardacre2015} as well as \citet{ACP:Luhar2017}. \citep{AE:Derwent2018} Uncertainties in surface ozone sources and sinks larger than in formulations? -> Need to read this one...
\begin{figure*}[t]
  \includegraphics[width=12cm]{pictures/final-total_ozone_drydep}\\
  \includegraphics[width=12cm]{pictures/final-total_ozone_drydepvelo}
  \caption{Comparison of various model runs with the OsloCTM3 and the multi-model-mean results by \citet{ACP:Hardacre2015}. (a) total annual ozone drydeposition; (b) annual average ozone dry depositon velocity.}
\end{figure*}
%
\begin{figure}[t]
  \includegraphics[width=8.3cm]{pictures/final-total_ozone_drydep_hem}
  \caption{Seasonal cycle of total amount of ozone removed from the atmosphere through dry deposition seperated into northern hemisphere (NH), tropics (TR), and southern hemisphere (SH). Comparison with results from \citet{ACP:Hardacre2015}.}
\end{figure}
%
\begin{figure}[t]
  \includegraphics[width=8.3cm]{pictures/final-total_ozone_drydep_monthly}\\
  \includegraphics[width=8.3cm]{pictures/final-total_ozone_drydepvelo_monthly}
  \caption{Comparison of monthly zonal distributions to results from \citep{ACP:Hardacre2015}. (a) Total amount of ozone removed from the atmosphere; (b) average ozone dry deposition velocitys.}
\end{figure}
%
\begin{figure}[t]
  \includegraphics[width=8.3cm]{pictures/final-total_ozone_drydepvelo_monthly_pft_nh}
  \caption{Average ozone dry deposition velocitys seperated by land use type and compared to results from \citep{ACP:Hardacre2015}.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with observations}
\label{subsec:obs}
The sites used in \citet{ACP:Hardacre2015} and additional ozone zonal data from satellites and sondes (\url{http://bodekerscientific.com/}). \citep{AE:Hu2017} -> need to look into this one...

\begin{figure}[t]
  \includegraphics[width=8.3cm]{pictures/final-monthly_ozone_drydep_stations_True}\\
  \includegraphics[width=8.3cm]{pictures/final-monthly_drydep_divergence_True}
  \caption{Ozone dry deposition velocities at different observation sites. Comparison between Weseley scheme and average result from all sensitivity tests to observations and multi-model-mean from \citet{ACP:Hardacre2015}.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
\label{sec:disc}
